---
title: "Fall 2019 - Data 607 - Week 1 Lab"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Charlie Rosemond - 082919

### Read in comma-delimited file as a data frame

Upon downloading the bridges.data.version2 file (https://archive.ics.uci.edu/ml/machine-learning-databases/bridges/bridges.data.version2) and uploading it to github, I read the raw file into R as a data frame called "bridges". I then check its top six rows.

```{r bridges.data 1}
bridges <- read.csv("https://raw.githubusercontent.com/chrosemo/data607_fall19_week1/master/bridges.data.version2", header = FALSE)
head(bridges)
```

### Update the data frame with appropriate column names

I update the column names of "bridges" to reflect the names noted in the bridges.names file (https://archive.ics.uci.edu/ml/machine-learning-databases/bridges/bridges.names) and again check the top six rows.

```{r bridges.data 2}
colnames(bridges) <- c("identifier", "river", "location", "erected", "purpose", "length", "lanes", "clear_g", "t_or_d", "material", "span", "rel_l", "type")
head(bridges)
```

### Subset the data frame

Lastly, I subset the data frame, creating a new one called "bridges_working" that keeps four columns. I then check the new data frame's bottom six rows.

```{r bridges.data 3}
bridges_working <- bridges[c("identifier", "river", "material", "span")]
tail(bridges_working)
```

